Analysis Report

### 2020-01-31 analysis/analysis_report.rmd
simplify for Binder

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.duplicate.label = 'allow')
library(tidyverse)
library(R.matlab)
library(afex)
library(emmeans)
library(here)
library(patchwork)
library(cowplot)
library(BayesFactor)
library(hrbrthemes)
library(ggsignif)
library(summarytools)

@@

#st_options(bootstrap.css     = FALSE,       # Already part of the theme so no need for it
#           plain.ascii       = FALSE,       # One of the essential settings
#           style             = "rmarkdown", # Idem.
#           dfSummary.silent  = TRUE,        # Suppresses messages about temporary files
#           footnote          = NA,          # Keeping the results minimalistic
#           subtitle.emphasis = FALSE)       # For the vignette theme, this gives
                                            # much better results. Your mileage may vary.

# st_css()

@@

vmacCols <- vmac_pal()
my_theme <- theme_ipsum_rc(grid = F, axis_title_just = "c", axis_title_size = 14, axis_text_size = 12, strip_text_size = 14, plot_title_size = 14, subtitle_size = 14, ticks = T) +
  theme(legend.position = "none", 
        plot.margin = margin(.5,1,.5,1,"cm"),
        axis.line = element_line(colour = "black", size = .5),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_line(colour = "black", size = .5),
        #aspect.ratio = 1.1,
        plot.tag = element_text(size = 20, family = font_rc),
        axis.title = element_text(margin = margin(12,1,1,1, unit = "cm")),
        axis.text.x = element_text(margin = margin(t = 4, unit = 'pt'), colour = 'black'),
        axis.text.y = element_text(margin = margin(r = 4, unit = 'pt'), colour = 'black'),
        axis.title.x = element_text(margin = margin(t = 8, unit = 'pt')),
        axis.title.y = element_text(margin = margin(r = 8, unit = 'pt')),
        legend.text = element_text(size = 14),
        legend.title = element_text(size = 14))

@@

This is the data set that we are left with:

```{r Glimpse exptdata after exclusions}
print(dfSummary(exptdata, style = "grid", graph.magnif = 0.75, tmp.img.dir = "/tmp"),  max.tbl.height = 300, method = "render")
```

Key for each of the variables in the table:

@@

Draw a graph of omission trials for each condition:

```{r Omission Trial Graph, fig.height=10, fig.width=5.5, message=FALSE, warning=FALSE, echo=FALSE}
omissionPlot_singleton <- exptdata %>%
  filter(condition == "Singleton Search") %>%
  group_by(sub, dType) %>%
  summarise(m = mean(omissionTrial)) %>%
  ggplot(aes(x = dType, y = m, fill = dType, shape = dType)) +
  geom_errorbar(data = filter(exptdata_means_bycondition, condition == "Singleton Search"), aes(x = dType, y = m, ymin = m-se, ymax = m+se), colour = "black", width = .15) +
  geom_line(aes(group = sub), colour = "black", alpha = .1, linetype = "solid", size = .5) +
  geom_line(data = filter(exptdata_means_bycondition, condition == "Singleton Search"), aes(x = dType, y = m, group = 1), colour = "black") + 
  geom_point(data = filter(exptdata_means_bycondition, condition == "Singleton Search"), aes(x = dType, y = m), colour = "black", size = 3) +
  geom_signif(comparisons = list(c("High", "Low"), c("Low", "Absent")), annotations = c("***","*"), y_position = c(.61,.57), colour = "black", tip_length = 0) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = c(0,0), limits = c(0,.8)) +
  scale_x_discrete(labels = c("High\nreward", "Low\nreward", "Distractor\nabsent")) +
  scale_fill_manual(values = vmacCols) +
  scale_colour_manual(values = vmacCols) +
  scale_shape_manual(name = "Trial Type", guide = guide_legend(), values = c(21,22,23)) +
  labs(y = "% Reward Omissions", x = "Trial Type", tag = "A", title = "Singleton Search") +
  my_theme

omissionPlot_feature <- 
  exptdata %>%
  filter(condition == "Feature Search") %>%
  group_by(sub, dType) %>%
  summarise(m = mean(omissionTrial)) %>%
  ggplot(aes(x = dType, y = m, fill = dType, shape = dType)) +
  geom_line(aes(group = sub), colour = "black", alpha = .1, linetype = "solid", size = .5) +
  geom_errorbar(data = filter(exptdata_means_bycondition, condition == "Feature Search"), aes(x = dType, y = m, ymin = m-se, ymax = m+se), colour = "black", width = .15) +
  geom_line(data = filter(exptdata_means_bycondition, condition == "Feature Search"), aes(x = dType, y = m, group = 1), colour = "black") + 
  geom_point(data = filter(exptdata_means_bycondition, condition == "Feature Search"), aes(x = dType, y = m), colour = "black", size = 3) +
  geom_signif(comparisons = list(c("High", "Low"), c("Low", "Absent")), annotations = c("***","***"), y_position = c(.61,.57), colour = "black", tip_length = 0) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = c(0,0), limits = c(0,.8)) +
  scale_x_discrete(labels = c("High\nreward", "Low\nreward", "Distractor\nabsent")) +
  scale_fill_manual(values = vmacCols) +
  scale_shape_manual(name = "Distractor Type", guide = guide_legend(), values = c(21,22,23)) +
  labs(y = "% Reward Omissions", x = "Trial Type", tag = "B", title = "Feature Search") +
  my_theme

omissionPlot_ms <- omissionPlot_singleton / omissionPlot_feature

# save_plot(here::here("analysis", "figures", "omission_plot.png"), omissionPlot_ms, ncol = 1, nrow = 2, type = "cairo", base_aspect_ratio = 1.1, dpi = 300)

omissionPlot_ms

@@

```{r Glimpse saccadedata}
print(dfSummary(saccadedata, style = "grid", graph.magnif = 0.75, tmp.img.dir = "/tmp"),  max.tbl.height = 300, method = "render")
```

@@

Graph of the first saccade data and capture scores:

```{r First Saccade Direction - Plot, echo=FALSE, fig.height=10, fig.width=10, message=FALSE, warning=FALSE}
saccadePlot_singleton <- saccadeData_means_bycondition %>%
  filter(condition == "Singleton Search", dType != "Absent") %>%
  ggplot(aes(group = dType, y = proportionSaccades, fill = dType, x = stimType, shape = dType, colour = dType)) +
  geom_line(aes(linetype = dType, colour = dType), na.rm = T, size = .5, position = position_dodge(width = .6)) +
  geom_point(aes(group = dType, y = proportionSaccades, x = stimType), na.rm = T, size = 1.5, alpha = .3, stroke = F, data = filter(saccadePlotDataParticipants, condition == "Singleton Search", dType != "Absent"), position = position_jitterdodge(dodge.width = .6, jitter.width = .2)) +
  geom_errorbar(aes(ymin = proportionSaccades-se, ymax = proportionSaccades+se), na.rm = T, linetype = "solid", position = position_dodge(width = .6, preserve = "total"), show.legend = FALSE, colour = "black", width = .3) +
  geom_point(na.rm = T, size = 3, position = position_dodge(width = .6), colour = "black") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = c(0,0), limits = c(0,.8)) +
  scale_linetype_manual(name = "Trial Type", values = c("solid", "longdash", "dotdash"), guide = guide_legend(), labels = c("High-reward", "Low-reward")) +
  scale_fill_manual(name = "Trial Type", values = vmacCols, labels = c("High-reward", "Low-reward")) +
  scale_colour_manual(name = "Trial Type", values = vmacCols, labels = c("High-reward", "Low-reward")) +
  scale_shape_manual(name = "Trial Type", guide = guide_legend(), values = c(21,22,23), labels = c("High-reward", "Low-reward")) +
  ylab("% First Saccades") + xlab("Stimulus Type") + labs(tag = "A", title = "Singleton Search") +
  my_theme

saccadePlot_feature <- saccadeData_means_bycondition %>%
  filter(condition == "Feature Search", dType != "Absent") %>%
  ggplot(aes(group = dType, y = proportionSaccades, fill = dType, x = stimType, shape = dType, colour = dType)) +
  geom_line(aes(linetype = dType, colour = dType), na.rm = T, size = .5, position = position_dodge(width = .6)) +
  geom_point(aes(group = dType, y = proportionSaccades, x = stimType), na.rm = T, size = 1.5, alpha = .3, stroke = F, data = filter(saccadePlotDataParticipants, condition == "Feature Search", dType != "Absent"), position = position_jitterdodge(dodge.width = .6, jitter.width = .2)) +
  geom_errorbar(aes(ymin = proportionSaccades-se, ymax = proportionSaccades+se), na.rm = T, linetype = "solid", position = position_dodge(width = .6, preserve = "total"), show.legend = FALSE, colour = "black", width = .3) +
  geom_point(na.rm = T, size = 3, position = position_dodge(width = .6), colour = "black") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = c(0,0), limits = c(0,.8)) +
  scale_linetype_manual(name = "Distractor Type", values = c("solid", "longdash", "dotdash"), guide = guide_legend()) +
  scale_fill_manual(name = "Distractor Type", values = vmacCols) +
  scale_colour_manual(name = "Distractor Type", values = vmacCols) +
  scale_shape_manual(name = "Distractor Type", guide = guide_legend(), values = c(21,22,23)) +
  ylab("% First Saccades") + xlab("Stimulus Type") + labs(tag = "C", title = "Feature Search") +
  my_theme

legend_saccade <- get_legend(saccadePlot_singleton + theme(legend.position = "bottom",
                                                           legend.title = element_text(size = 14),
                                                           legend.text = element_text(size = 14),
                                                           legend.key.width = unit(24, 'pt')))

## Capture Bar Plots
captureBarPlot_singleton <- captureMeans %>%
  filter(condition == "Singleton Search") %>%
  mutate(annotation = c("***", " ")) %>%
  ggplot(aes(x = dType, y = Capture, fill = dType)) +
  annotate(geom = "text", label = "Capture", x = 2.85, y = .15, angle = 90, vjust = 1, hjust = .5, family = font_rc) +
  annotate(geom = "text", label = "Suppression", x = 2.85, y = -.15, angle = 90, vjust = 1, hjust = .5, family = font_rc) +
  annotate(geom = "segment", x = 2.65, xend = 2.65, y = -.03, yend = -.27, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) +
  annotate(geom = "segment", x = 2.65, xend = 2.65, y = .03, yend = .27, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) +
  geom_col(position = position_dodge(.9), size = .3) +
  geom_hline(yintercept = 0, color = "black", size = .5) +
  geom_errorbar(aes(ymax = Capture + se, ymin = Capture - se), position = position_dodge(.9), width = .1) +
  geom_text(aes(label = annotation), nudge_y = .05) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = c(0,0), limits = c(-.3001, .3001)) +
  scale_x_discrete(labels = c("High\nreward", "Low\nreward")) +
  coord_cartesian(xlim = c(1,2),
                  clip = 'off') +
  scale_fill_manual(name = "Distractor Type", values = vmacCols, guide = guide_legend()) +
  ylab("Capture Score") + xlab("Trial Type") + labs(tag = "B") +
  my_theme

captureBarPlot_feature <- 
  captureMeans %>%
  filter(condition == "Feature Search") %>%
  mutate(annotation = c("***", "*")) %>%
  ggplot(aes(x = dType, y = Capture, fill = dType)) +
  annotate(geom = "text", label = "Capture", x = 2.85, y = .15, angle = 90, vjust = 1, hjust = .5, family = font_rc) +
  annotate(geom = "text", label = "Suppression", x = 2.85, y = -.15, angle = 90, vjust = 1, hjust = .5, family = font_rc) +
  annotate(geom = "segment", x = 2.65, xend = 2.65, y = -.03, yend = -.27, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) +
  annotate(geom = "segment", x = 2.65, xend = 2.65, y = .03, yend = .27, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) +
  geom_col(position = position_dodge(.9), size = .3) + 
  geom_hline(yintercept = 0, size = .5) +
  geom_errorbar(aes(ymax = Capture + se, ymin = Capture - se), position = position_dodge(.9), width = .1) +
  geom_text(aes(label = annotation), nudge_y = c(.05, .07)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = c(0,0), limits = c(-.3001, .3001)) +
  scale_x_discrete(labels = c("High\nreward", "Low\nreward")) +
  coord_cartesian(xlim = c(1,2),
                  clip = 'off') +
  scale_fill_manual(name = "Distractor Type", values = vmacCols, guide = guide_legend()) +
  ylab("Capture Score") + xlab("Trial Type") + labs(tag = "D") +
  my_theme

saccadePlot_ms_row1 <- saccadePlot_singleton + captureBarPlot_singleton + plot_spacer() + plot_layout(nrow = 1, widths = c(2.2,1,.1))

saccadePlot_ms_row2 <- saccadePlot_feature + captureBarPlot_feature + plot_spacer() + plot_layout(nrow = 1, widths = c(2,1,.1))

saccadePlot_ms <- saccadePlot_ms_row1 / legend_saccade / saccadePlot_ms_row2 + plot_layout(heights = c(1,.1,1))

 # save_plot(here("analysis", "figures", "saccade_plot.png"), saccadePlot_ms, ncol = 2.2, nrow = 2, type = "cairo", base_aspect_ratio = .9, dpi = 300)

saccadePlot_ms
```

@@

```{r Block Analysis Graph, echo=FALSE, fig.height=10, fig.width=5, message=FALSE, warning=FALSE}
capturePlot_byblock_singleton <- 
  capturemeans_byblock %>%
  filter(condition == "Singleton Search") %>%
  ggplot(aes(x = newblock, y = capture, group = dType, shape = dType, colour = dType)) +
  #geom_rect(fill = "#D3D3D3", xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = 0, alpha = .3, inherit.aes = F) +
  geom_hline(yintercept = 0, colour = "black", size = .5, linetype = "dotted") +
  annotate(geom = "text", label = "Capture", x = 4.7, y = .15, angle = 90, vjust = 1, hjust = .5, family = font_rc) +
  annotate(geom = "text", label = "Suppression", x = 4.7, y = -.15, angle = 90, vjust = 1, hjust = .5, family = font_rc) +
  annotate(geom = "segment", x = 4.5, xend = 4.5, y = -.03, yend = -.27, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) +
  annotate(geom = "segment", x = 4.5, xend = 4.5, y = .03, yend = .27, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) +
  geom_line(aes(linetype = dType), size = .5) +
  geom_errorbar(aes(ymin = capture - se, ymax = capture + se), width = .1, colour = "black") +
  geom_point(aes(shape = dType, fill = dType), size = 3, colour = "black") +
  scale_shape_manual(name = "Distractor Type", guide = guide_legend(), values = c(21,22)) +
  scale_fill_manual(name = "Distractor Type", values = vmacCols, guide = guide_legend()) +
  scale_colour_manual(name = "Distractor Type", values = vmacCols, guide = guide_legend()) +
  scale_y_continuous(expand = c(0,0), limits = c(-.3,.301), breaks = seq(-.3, .3, .1), labels = scales::percent_format(accuracy = 1)) +
  scale_x_discrete() +
  coord_cartesian(xlim = c(1,4),
                  clip = 'off') +
  scale_linetype_manual(name = "Distractor Type", values = c("solid", "longdash"), guide = guide_legend()) +
  ylab("Capture Score") + xlab("Epoch (96 trials)") + labs(tag = "A", title = 'Singleton Search') +
  my_theme

>>>>

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.duplicate.label = 'allow')
library(tidyverse)
library(R.matlab)
library(afex)
library(emmeans)
library(here)
library(BayesFactor)

@@

@@

# These packages are required for producing the figures. Commenting out to try and simplify the project for Binder
#library(patchwork)
#library(cowplot)
#
#library(hrbrthemes)
#library(ggsignif)
#library(summarytools)

#vmacCols <- vmac_pal()
#my_theme <- theme_ipsum_rc(grid = F, axis_title_just = "c", axis_title_size = 14, axis_text_size = 12, strip_text_size = 14, plot_title_size = 14, subtitle_size = 14, ticks = T) +
#  theme(legend.position = "none", 
        # plot.margin = margin(.5,1,.5,1,"cm"),
        # axis.line = element_line(colour = "black", size = .5),
        # axis.ticks.x = element_blank(),
        # axis.ticks.y = element_line(colour = "black", size = .5),
        # #aspect.ratio = 1.1,
        # plot.tag = element_text(size = 20, family = font_rc),
        # axis.title = element_text(margin = margin(12,1,1,1, unit = "cm")),
        # axis.text.x = element_text(margin = margin(t = 4, unit = 'pt'), colour = 'black'),
        # axis.text.y = element_text(margin = margin(r = 4, unit = 'pt'), colour = 'black'),
        # axis.title.x = element_text(margin = margin(t = 8, unit = 'pt')),
        # axis.title.y = element_text(margin = margin(r = 8, unit = 'pt')),
        # legend.text = element_text(size = 14),
        # legend.title = element_text(size = 14))

@@

<!-- This is the data set that we are left with: -->

<!-- ```{r Glimpse exptdata after exclusions} -->
<!-- print(dfSummary(exptdata, style = "grid", graph.magnif = 0.75, tmp.img.dir = "/tmp"),  max.tbl.height = 300, method = "render") -->
<!-- ``` -->

Key for each of the variables in the df:

@@

<!-- Draw a graph of omission trials for each condition: -->

<!-- ```{r Omission Trial Graph, fig.height=10, fig.width=5.5, message=FALSE, warning=FALSE, echo=FALSE} -->
<!-- omissionPlot_singleton <- exptdata %>% -->
<!--   filter(condition == "Singleton Search") %>% -->
<!--   group_by(sub, dType) %>% -->
<!--   summarise(m = mean(omissionTrial)) %>% -->
<!--   ggplot(aes(x = dType, y = m, fill = dType, shape = dType)) + -->
<!--   geom_errorbar(data = filter(exptdata_means_bycondition, condition == "Singleton Search"), aes(x = dType, y = m, ymin = m-se, ymax = m+se), colour = "black", width = .15) + -->
<!--   geom_line(aes(group = sub), colour = "black", alpha = .1, linetype = "solid", size = .5) + -->
<!--   geom_line(data = filter(exptdata_means_bycondition, condition == "Singleton Search"), aes(x = dType, y = m, group = 1), colour = "black") +  -->
<!--   geom_point(data = filter(exptdata_means_bycondition, condition == "Singleton Search"), aes(x = dType, y = m), colour = "black", size = 3) + -->
<!--   geom_signif(comparisons = list(c("High", "Low"), c("Low", "Absent")), annotations = c("***","*"), y_position = c(.61,.57), colour = "black", tip_length = 0) + -->
<!--   scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = c(0,0), limits = c(0,.8)) + -->
<!--   scale_x_discrete(labels = c("High\nreward", "Low\nreward", "Distractor\nabsent")) + -->
<!--   scale_fill_manual(values = vmacCols) + -->
<!--   scale_colour_manual(values = vmacCols) + -->
<!--   scale_shape_manual(name = "Trial Type", guide = guide_legend(), values = c(21,22,23)) + -->
<!--   labs(y = "% Reward Omissions", x = "Trial Type", tag = "A", title = "Singleton Search") + -->
<!--   my_theme -->

<!-- omissionPlot_feature <-  -->
<!--   exptdata %>% -->
<!--   filter(condition == "Feature Search") %>% -->
<!--   group_by(sub, dType) %>% -->
<!--   summarise(m = mean(omissionTrial)) %>% -->
<!--   ggplot(aes(x = dType, y = m, fill = dType, shape = dType)) + -->
<!--   geom_line(aes(group = sub), colour = "black", alpha = .1, linetype = "solid", size = .5) + -->
<!--   geom_errorbar(data = filter(exptdata_means_bycondition, condition == "Feature Search"), aes(x = dType, y = m, ymin = m-se, ymax = m+se), colour = "black", width = .15) + -->
<!--   geom_line(data = filter(exptdata_means_bycondition, condition == "Feature Search"), aes(x = dType, y = m, group = 1), colour = "black") +  -->
<!--   geom_point(data = filter(exptdata_means_bycondition, condition == "Feature Search"), aes(x = dType, y = m), colour = "black", size = 3) + -->
<!--   geom_signif(comparisons = list(c("High", "Low"), c("Low", "Absent")), annotations = c("***","***"), y_position = c(.61,.57), colour = "black", tip_length = 0) + -->
<!--   scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = c(0,0), limits = c(0,.8)) + -->
<!--   scale_x_discrete(labels = c("High\nreward", "Low\nreward", "Distractor\nabsent")) + -->
<!--   scale_fill_manual(values = vmacCols) + -->
<!--   scale_shape_manual(name = "Distractor Type", guide = guide_legend(), values = c(21,22,23)) + -->
<!--   labs(y = "% Reward Omissions", x = "Trial Type", tag = "B", title = "Feature Search") + -->
<!--   my_theme -->

<!-- omissionPlot_ms <- omissionPlot_singleton / omissionPlot_feature -->

<!-- # save_plot(here::here("analysis", "figures", "omission_plot.png"), omissionPlot_ms, ncol = 1, nrow = 2, type = "cairo", base_aspect_ratio = 1.1, dpi = 300) -->

<!-- omissionPlot_ms -->

<!-- ``` -->

@@

<!-- ```{r Glimpse saccadedata} -->
<!-- print(dfSummary(saccadedata, style = "grid", graph.magnif = 0.75, tmp.img.dir = "/tmp"),  max.tbl.height = 300, method = "render") -->
<!-- ``` -->

@@

<!-- Graph of the first saccade data and capture scores: -->

<!-- ```{r First Saccade Direction - Plot, echo=FALSE, fig.height=10, fig.width=10, message=FALSE, warning=FALSE} -->
<!-- saccadePlot_singleton <- saccadeData_means_bycondition %>% -->
<!--   filter(condition == "Singleton Search", dType != "Absent") %>% -->
<!--   ggplot(aes(group = dType, y = proportionSaccades, fill = dType, x = stimType, shape = dType, colour = dType)) + -->
<!--   geom_line(aes(linetype = dType, colour = dType), na.rm = T, size = .5, position = position_dodge(width = .6)) + -->
<!--   geom_point(aes(group = dType, y = proportionSaccades, x = stimType), na.rm = T, size = 1.5, alpha = .3, stroke = F, data = filter(saccadePlotDataParticipants, condition == "Singleton Search", dType != "Absent"), position = position_jitterdodge(dodge.width = .6, jitter.width = .2)) + -->
<!--   geom_errorbar(aes(ymin = proportionSaccades-se, ymax = proportionSaccades+se), na.rm = T, linetype = "solid", position = position_dodge(width = .6, preserve = "total"), show.legend = FALSE, colour = "black", width = .3) + -->
<!--   geom_point(na.rm = T, size = 3, position = position_dodge(width = .6), colour = "black") + -->
<!--   scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = c(0,0), limits = c(0,.8)) + -->
<!--   scale_linetype_manual(name = "Trial Type", values = c("solid", "longdash", "dotdash"), guide = guide_legend(), labels = c("High-reward", "Low-reward")) + -->
<!--   scale_fill_manual(name = "Trial Type", values = vmacCols, labels = c("High-reward", "Low-reward")) + -->
<!--   scale_colour_manual(name = "Trial Type", values = vmacCols, labels = c("High-reward", "Low-reward")) + -->
<!--   scale_shape_manual(name = "Trial Type", guide = guide_legend(), values = c(21,22,23), labels = c("High-reward", "Low-reward")) + -->
<!--   ylab("% First Saccades") + xlab("Stimulus Type") + labs(tag = "A", title = "Singleton Search") + -->
<!--   my_theme -->

<!-- saccadePlot_feature <- saccadeData_means_bycondition %>% -->
<!--   filter(condition == "Feature Search", dType != "Absent") %>% -->
<!--   ggplot(aes(group = dType, y = proportionSaccades, fill = dType, x = stimType, shape = dType, colour = dType)) + -->
<!--   geom_line(aes(linetype = dType, colour = dType), na.rm = T, size = .5, position = position_dodge(width = .6)) + -->
<!--   geom_point(aes(group = dType, y = proportionSaccades, x = stimType), na.rm = T, size = 1.5, alpha = .3, stroke = F, data = filter(saccadePlotDataParticipants, condition == "Feature Search", dType != "Absent"), position = position_jitterdodge(dodge.width = .6, jitter.width = .2)) + -->
<!--   geom_errorbar(aes(ymin = proportionSaccades-se, ymax = proportionSaccades+se), na.rm = T, linetype = "solid", position = position_dodge(width = .6, preserve = "total"), show.legend = FALSE, colour = "black", width = .3) + -->
<!--   geom_point(na.rm = T, size = 3, position = position_dodge(width = .6), colour = "black") + -->
<!--   scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = c(0,0), limits = c(0,.8)) + -->
<!--   scale_linetype_manual(name = "Distractor Type", values = c("solid", "longdash", "dotdash"), guide = guide_legend()) + -->
<!--   scale_fill_manual(name = "Distractor Type", values = vmacCols) + -->
<!--   scale_colour_manual(name = "Distractor Type", values = vmacCols) + -->
<!--   scale_shape_manual(name = "Distractor Type", guide = guide_legend(), values = c(21,22,23)) + -->
<!--   ylab("% First Saccades") + xlab("Stimulus Type") + labs(tag = "C", title = "Feature Search") + -->
<!--   my_theme -->

<!-- legend_saccade <- get_legend(saccadePlot_singleton + theme(legend.position = "bottom", -->
<!--                                                            legend.title = element_text(size = 14), -->
<!--                                                            legend.text = element_text(size = 14), -->
<!--                                                            legend.key.width = unit(24, 'pt'))) -->

<!-- ## Capture Bar Plots -->
<!-- captureBarPlot_singleton <- captureMeans %>% -->
<!--   filter(condition == "Singleton Search") %>% -->
<!--   mutate(annotation = c("***", " ")) %>% -->
<!--   ggplot(aes(x = dType, y = Capture, fill = dType)) + -->
<!--   annotate(geom = "text", label = "Capture", x = 2.85, y = .15, angle = 90, vjust = 1, hjust = .5, family = font_rc) + -->
<!--   annotate(geom = "text", label = "Suppression", x = 2.85, y = -.15, angle = 90, vjust = 1, hjust = .5, family = font_rc) + -->
<!--   annotate(geom = "segment", x = 2.65, xend = 2.65, y = -.03, yend = -.27, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) + -->
<!--   annotate(geom = "segment", x = 2.65, xend = 2.65, y = .03, yend = .27, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) + -->
<!--   geom_col(position = position_dodge(.9), size = .3) + -->
<!--   geom_hline(yintercept = 0, color = "black", size = .5) + -->
<!--   geom_errorbar(aes(ymax = Capture + se, ymin = Capture - se), position = position_dodge(.9), width = .1) + -->
<!--   geom_text(aes(label = annotation), nudge_y = .05) + -->
<!--   scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = c(0,0), limits = c(-.3001, .3001)) + -->
<!--   scale_x_discrete(labels = c("High\nreward", "Low\nreward")) + -->
<!--   coord_cartesian(xlim = c(1,2), -->
<!--                   clip = 'off') + -->
<!--   scale_fill_manual(name = "Distractor Type", values = vmacCols, guide = guide_legend()) + -->
<!--   ylab("Capture Score") + xlab("Trial Type") + labs(tag = "B") + -->
<!--   my_theme  -->

<!-- captureBarPlot_feature <-  -->
<!--   captureMeans %>% -->
<!--   filter(condition == "Feature Search") %>% -->
<!--   mutate(annotation = c("***", "*")) %>% -->
<!--   ggplot(aes(x = dType, y = Capture, fill = dType)) + -->
<!--   annotate(geom = "text", label = "Capture", x = 2.85, y = .15, angle = 90, vjust = 1, hjust = .5, family = font_rc) + -->
<!--   annotate(geom = "text", label = "Suppression", x = 2.85, y = -.15, angle = 90, vjust = 1, hjust = .5, family = font_rc) + -->
<!--   annotate(geom = "segment", x = 2.65, xend = 2.65, y = -.03, yend = -.27, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) + -->
<!--   annotate(geom = "segment", x = 2.65, xend = 2.65, y = .03, yend = .27, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) + -->
<!--   geom_col(position = position_dodge(.9), size = .3) +  -->
<!--   geom_hline(yintercept = 0, size = .5) + -->
<!--   geom_errorbar(aes(ymax = Capture + se, ymin = Capture - se), position = position_dodge(.9), width = .1) + -->
<!--   geom_text(aes(label = annotation), nudge_y = c(.05, .07)) + -->
<!--   scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = c(0,0), limits = c(-.3001, .3001)) + -->
<!--   scale_x_discrete(labels = c("High\nreward", "Low\nreward")) + -->
<!--   coord_cartesian(xlim = c(1,2), -->
<!--                   clip = 'off') + -->
<!--   scale_fill_manual(name = "Distractor Type", values = vmacCols, guide = guide_legend()) + -->
<!--   ylab("Capture Score") + xlab("Trial Type") + labs(tag = "D") + -->
<!--   my_theme -->

<!-- saccadePlot_ms_row1 <- saccadePlot_singleton + captureBarPlot_singleton + plot_spacer() + plot_layout(nrow = 1, widths = c(2.2,1,.1)) -->

<!-- saccadePlot_ms_row2 <- saccadePlot_feature + captureBarPlot_feature + plot_spacer() + plot_layout(nrow = 1, widths = c(2,1,.1)) -->

<!-- saccadePlot_ms <- saccadePlot_ms_row1 / legend_saccade / saccadePlot_ms_row2 + plot_layout(heights = c(1,.1,1)) -->

<!--  # save_plot(here("analysis", "figures", "saccade_plot.png"), saccadePlot_ms, ncol = 2.2, nrow = 2, type = "cairo", base_aspect_ratio = .9, dpi = 300) -->

<!-- saccadePlot_ms -->
<!-- ``` -->

@@

<!-- ```{r Block Analysis Graph, echo=FALSE, fig.height=10, fig.width=5, message=FALSE, warning=FALSE} -->
<!-- capturePlot_byblock_singleton <-  -->
<!--   capturemeans_byblock %>% -->
<!--   filter(condition == "Singleton Search") %>% -->
<!--   ggplot(aes(x = newblock, y = capture, group = dType, shape = dType, colour = dType)) + -->
<!--   #geom_rect(fill = "#D3D3D3", xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = 0, alpha = .3, inherit.aes = F) + -->
<!--   geom_hline(yintercept = 0, colour = "black", size = .5, linetype = "dotted") + -->
<!--   annotate(geom = "text", label = "Capture", x = 4.7, y = .15, angle = 90, vjust = 1, hjust = .5, family = font_rc) + -->
<!--   annotate(geom = "text", label = "Suppression", x = 4.7, y = -.15, angle = 90, vjust = 1, hjust = .5, family = font_rc) + -->
<!--   annotate(geom = "segment", x = 4.5, xend = 4.5, y = -.03, yend = -.27, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) + -->
<!--   annotate(geom = "segment", x = 4.5, xend = 4.5, y = .03, yend = .27, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) + -->
<!--   geom_line(aes(linetype = dType), size = .5) + -->
<!--   geom_errorbar(aes(ymin = capture - se, ymax = capture + se), width = .1, colour = "black") + -->
<!--   geom_point(aes(shape = dType, fill = dType), size = 3, colour = "black") + -->
<!--   scale_shape_manual(name = "Distractor Type", guide = guide_legend(), values = c(21,22)) + -->
<!--   scale_fill_manual(name = "Distractor Type", values = vmacCols, guide = guide_legend()) + -->
<!--   scale_colour_manual(name = "Distractor Type", values = vmacCols, guide = guide_legend()) + -->
<!--   scale_y_continuous(expand = c(0,0), limits = c(-.3,.301), breaks = seq(-.3, .3, .1), labels = scales::percent_format(accuracy = 1)) + -->
<!--   scale_x_discrete() + -->
<!--   coord_cartesian(xlim = c(1,4), -->
<!--                   clip = 'off') + -->
<!--   scale_linetype_manual(name = "Distractor Type", values = c("solid", "longdash"), guide = guide_legend()) + -->
<!--   ylab("Capture Score") + xlab("Epoch (96 trials)") + labs(tag = "A", title = 'Singleton Search') + -->
<!--   my_theme -->

<!-- capturePlot_byblock_feature <-  -->
<!--   capturemeans_byblock %>% -->
<!--   filter(condition == "Feature Search") %>% -->
<!--   ggplot(aes(x = newblock, y = capture, group = dType, shape = dType, colour = dType)) + -->
<!--   geom_hline(yintercept = 0, colour = "black", size = .5, linetype = "dotted") + -->
<!--   annotate(geom = "text", label = "Capture", x = 4.7, y = .15, angle = 90, vjust = 1, hjust = .5, family = font_rc) + -->
<!--   annotate(geom = "text", label = "Suppression", x = 4.7, y = -.15, angle = 90, vjust = 1, hjust = .5, family = font_rc) + -->
<!--   annotate(geom = "segment", x = 4.5, xend = 4.5, y = -.03, yend = -.27, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) + -->
<!--   annotate(geom = "segment", x = 4.5, xend = 4.5, y = .03, yend = .27, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) + -->
<!--   geom_line(aes(linetype = dType), size = .5) + -->
<!--   geom_errorbar(aes(ymin = capture - se, ymax = capture + se), width = .1, colour = "black") + -->
<!--   geom_point(aes(shape = dType, fill = dType), size = 3, colour = "black") + -->
<!--   scale_shape_manual(name = "Distractor Type", guide = guide_legend(), values = c(21,22)) + -->
<!--   scale_fill_manual(name = "Distractor Type", values = vmacCols, guide = guide_legend()) + -->
<!--   scale_colour_manual(name = "Distractor Type", values = vmacCols, guide = guide_legend()) + -->
<!--   scale_y_continuous(expand = c(0,0), limits = c(-.3,.301), breaks = seq(-.3, .3, .1), labels = scales::percent_format(accuracy = 1)) + -->
<!--   scale_x_discrete() + -->
<!--   coord_cartesian(xlim = c(1,4), -->
<!--                   clip = 'off') + -->
<!--   scale_linetype_manual(name = "Distractor Type", values = c("solid", "longdash"), guide = guide_legend()) + -->
<!--   ylab("Capture Score") + xlab("Epoch (96 trials)") + labs(tag = "B", title = 'Feature Search') + -->
<!--   my_theme -->
